Project Report\\\textsc{DEVS Ex Machina}

### 2015-05-25 manual/projectrapport.tex
Added ADEVS comparison to performance analysis

\chapter{Performance analysis}
To measure the performance of \textsc{DEVS Ex Machina} under more demanding conditions, \textbf{DEVStone} and \textbf{PHOLD} benchmarks were used. Every time we compare the performance of our implementation with \textit{PythonPDEVS}.\\

\section{Classic DEVS}
Using Classic DEVS we see noticeable speedups compared to PyPDEVS. The tests are completed in far less time, using the CPU more effici\"ently.

@@

 Performance counter stats for 'python experiment.py def 2 false':

@@

       0.021871681 seconds time elapsed
\end{Verbatim}
\paragraph{\textsc{PythonPDEVS}}
\begin{Verbatim}[fontsize=\small]
$ perf stat python experiment.py def 2 false > out.txt

 Performance counter stats for 'python experiment.py def 2 false':

@@

     156.945218942 seconds time elapsed
\end{Verbatim}
\paragraph{\textsc{PythonPDEVS}}
\begin{Verbatim}[fontsize=\small]
$ perf stat mpirun -np 2 python experiment.py def 2 false > out.txt

 Performance counter stats for 'mpirun -np 2 python experiment.py def 2 false':

@@

>>>>

\chapter{Performance analysis}
To measure the performance of \textsc{DEVS Ex Machina} under more demanding conditions, \textbf{DEVStone} and \textbf{PHOLD} benchmarks were used. Every time we compare the performance of our implementation with \textit{PythonPDEVS}.\\
Note: at the time, no major research has gone into the use of several compiler optimizations. Potentially, there is still speed to be gained here.\\
\\
{\footnotesize[All the following tests were performed using an \textit{Intel Core i5 M520} CPU at 2.40GHz with 4GB RAM]}

\section{Classic DEVS}
Using Classic DEVS we see noticeable speedups compared to PyPDEVS. The tests are completed in far less time, using the CPU more efficiently.

\subsection{DEVStone}
The DEVStone benchmark used for both implementations has a width of 2 and a depth of 3.
\paragraph{\textsc{DEVS Ex Machina}}
\begin{Verbatim}[fontsize=\small]
$ perf stat ./dxexmachina_devstone

@@

 Performance counter stats for 'python experiment.py default 2 false':

@@

       0.021871681 seconds time elapsed
\end{Verbatim}
\paragraph{\textsc{PythonPDEVS}}
\begin{Verbatim}[fontsize=\small]
$ perf stat python experiment.py default 2 false > out.txt

 Performance counter stats for 'python experiment.py default 2 false':

@@

     156.945218942 seconds time elapsed
\end{Verbatim}
\paragraph{\textsc{PythonPDEVS}}
\begin{Verbatim}[fontsize=\small]
$ perf stat mpirun -np 2 python experiment.py default 2 false > out.txt

 Performance counter stats for 'mpirun -np 2 python experiment.py default 2 false':

@@

\section{Compared to \textsc{ADEVS}}
Since the DEVStone benchmark for \textsc{ADEVS} does not support different depths, a test with greater width was performed instead.\\
As we can see, \textsc{ADEVS} is still quite a bit faster, though its CPU usage is less efficient.
\paragraph{\textsc{DEVS Ex Machina} - Classic DEVS}
\begin{Verbatim}[fontsize=\small]
$ perf stat ./dxexmachina_devstone 32 0

 Performance counter stats for './dxexmachina_devstone 32 0':

        836.066726 task-clock (msec)         #    1.113 CPUs utilized          
             1,241 context-switches          #    0.001 M/sec                  
             1,027 cpu-migrations            #    0.001 M/sec                  
               720 page-faults               #    0.861 K/sec                  
     2,278,424,999 cycles                    #    2.725 GHz                     [84.52%]
       959,881,005 stalled-cycles-frontend   #   42.13% frontend cycles idle    [84.53%]
       500,732,097 stalled-cycles-backend    #   21.98% backend  cycles idle    [68.69%]
     2,775,228,039 instructions              #    1.22  insns per cycle        
                                             #    0.35  stalled cycles per insn [85.11%]
       654,396,817 branches                  #  782.709 M/sec                   [84.56%]
         9,222,451 branch-misses             #    1.41% of all branches         [83.94%]

       0.750984696 seconds time elapsed
\end{Verbatim}
\paragraph{\textsc{ADEVS} - Classic DEVS}
\begin{Verbatim}[fontsize=\small]
$ perf stat ./sim 32 0

 Performance counter stats for './sim 32 0':

         15.465233 task-clock (msec)         #    0.976 CPUs utilized          
                 1 context-switches          #    0.065 K/sec                  
                 1 cpu-migrations            #    0.065 K/sec                  
               340 page-faults               #    0.022 M/sec                  
        22,395,954 cycles                    #    1.448 GHz                     [74.20%]
         6,618,757 stalled-cycles-frontend   #   29.55% frontend cycles idle    [74.17%]
         2,895,009 stalled-cycles-backend    #   12.93% backend  cycles idle    [87.88%]
        31,797,999 instructions              #    1.42  insns per cycle        
                                             #    0.21  stalled cycles per insn
         6,645,494 branches                  #  429.705 M/sec                  
           250,467 branch-misses             #    3.77% of all branches         [74.03%]

       0.015852985 seconds time elapsed
\end{Verbatim}
